A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-07 manuscript.Rmd
some amendments to the intro

With the R version that you currently use, this specification is then translated into a `Dockerfile` that makes sure that the container image has all these packages installed.
The `Dockerfile` also contains the current date and fixes packages versions to the version of the package that were available on that day on the [Comprehensive R Archive Network (CRAN)](https://cran.r-project.org)[^cran] by relying on the [CRAN timemachine of Microsoft R Application Network (MRAN)](https://mran.microsoft.com/timemachine)[^mran].
<!-- Hands on: Introduce Docker -->

@@

[^cran]: https://cran.r-project.org
[^mran]: https://mran.microsoft.com/timemachine

>>>>

With the R version that you currently use, this specification is then translated into a `Dockerfile` that makes sure that the container image has all these packages installed:
<!--AP: can you say something about ensuring a given version of the R package; can the header be automatically generated from a given R script?-->
<!-- Hands on: Introduce Docker -->

@@
